---
output: 
   pdf_document:
      df_print: kable
classoption: landscape
geometry: margin=0.25in
---

```{r sample, message=FALSE, warning=FALSE, include=FALSE}

library(knitr)
library(tidyverse)
library(kableExtra)
library(grid)
library(gridExtra)
library(magick)
library(multipanelfigure)

load("../data/ns_church_history.rdata")

```
# The History of the Reformed Church in the Parish of Neu-Schowe, 1786-1923
## by Daniel Gutsohn

Scanned and converted to text using Tesseract OCR and the "deu-frak" Fraktur training set

Translated to English using Google Translate

by Arthur Steinmetz, <apsteinmetz@yahoo.com>, July 2020

This presents the scanned image, text and translation side by side. Note the translation is pretty choppy because there is no human interpretation, just robots.  I present this in the hope that this will help others who might want to do a better job.
\newpage
```{r print_cover, echo=FALSE, fig.height=7.5, message=FALSE, warning=FALSE}

page_img_file <- "../img/Neu_Schowe_Church_00.jpg"
# instantiate
figure <- multi_panel_figure(
   columns = 1,
   rows = 1,
   panel_label_type = "none")


figure <- figure %>% 
   fill_panel(panel = page_img_file,scaling="fit")
cat(paste0("Page ",1))   
print(figure)
```

```{r print_body, echo=FALSE, fig.height=8, fig.width=11, message=FALSE, warning=FALSE}

print_page <- function(n){
   message(paste("Page",n))
   page_img_file <- paste0("../img/",NS_Church_History$img_file[n])
   page_text_de <- NS_Church_History$content[[n]][2]
   page_text_en <- NS_Church_History$content[[n]][3]
   # instantiate
   figure <- multi_panel_figure(
      columns = 3,
      rows = 1,
      panel_label_type = "none",
      column_spacing = 1)
   
   
   figure <- figure %>% 
      fill_panel(panel = page_img_file,scaling = "stretch",column = c(1)) %>% 
      fill_panel(tableGrob(page_text_de,
                           theme = ttheme_default(base_size = 7,padding = unit(c(1,2),"mm"))
      ),
      row= 1,column = 2,panel_clip = "off") %>% 
      fill_panel(tableGrob(page_text_en, 
                           theme = ttheme_default(base_size = 7,padding = unit(c(1,2),"mm")),
                           rows = NULL
      ),
      row= 1,column = 3,panel_clip = "off") 
   
   # return(bind_cols(rownames_to_column(page_text_de,var="Row"),page_text_en))
   cat(paste0("Page ",n+1))   
   print(figure)
}


nothing <- NS_Church_History$page_num %>% 
   as.numeric() %>% 
   walk(print_page)

```
